### 2016-08-12 latex/paper.tex
Remove .gitignore files

$^\dag$ Department of Civil Engineering\\
Northwestern University\\
2145 Sheridan Road, Evanston, IL 60208, USA\\
e-mail: o.balogun@northwestern.edu\\
\end{tabular}
\end{center}

@@

``If the wheel becomes untrue in two large waves during stress relieving, the maximum, safe tension has been exceeded. Approach this tension carefully to avoid major rim distortions. When the wheel loses alignment from stress relieving, loosen all spokes a half turn before retruing the wheel.''

@@

\section{GENERAL INSTRUCTIONS}

The paper must be written in English. It must contain the full name, address 
and e-mail address of each author. No hard limits on the total length of the 
paper are set, but it should better not exceed 20 pages. All page margins 
should be 3\,cm. The paper used should have the size 210\,x\,297\, mm 
which is the European (German) A4 size. It is suggested to use styles for 
formatting and automatic reference, figure numbering to avoid editorial 
errors. To avoid compatibility problems it is advised to use only upper or 
lower case Latin alphabet, numbers and the underscore character in the file 
name.

\subsection{Equations}

Equations should be numbered continuously according to the format shown in 
Equation~(\ref{eq:equ1}): 
\begin{equation} \label{eq:equ1}
  e^{i\pi} + 1 = 0, 
\end{equation}
where the unknown symbols are explained after the equation.

>>>>

$^\dag$ Department of Civil Engineering\\
Northwestern University\\
2145 Sheridan Road, Evanston, IL 60208, USA\\
e-mail: o-balogun@northwestern.edu\\
\end{tabular}
\end{center}

@@

\begin{quotation}
\noindent``If the wheel becomes untrue in two large waves during stress relieving, the maximum, safe tension has been exceeded. Approach this tension carefully to avoid major rim distortions. When the wheel loses alignment from stress relieving, loosen all spokes a half turn before retruing the wheel.''
\end{quotation}

@@

\section{DEFORMATION OF THE WHEEL}
\subsection{Rim equations}

The rim is modeled as an initially circular beam with a constant cross-section.

\subsection{Spoke equations}

In this paper we consider bicycle wheels with slender prestressed spokes. We model a single spoke as an elastic bar pinned at each end. This ensures that the spoke force is always collinear with the spoke axis. The linearized elongation of a spoke is given by
\begin{equation}\label{eq:elong}
\Delta l = (\bm{u}_2 - \bm{u}_1)\cdot \hat{\bm{n}}_0
\end{equation}
where $\bm{u}_1$ and $\bm{u}_2$ are the displacement vectors of the two nodes of the spoke and $\hat{\bm{n}}_0$ is a unit vector pointing from node 1 to node 2.
